### 2017-03-30 paper/intro.tex
minor changes on intro

At large organizations, the alternative of renting cloud
services\footnote{List of popular hosting cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures to running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware (\eg{}, existing workstations), emerges as an attractive
solution for running tests.  Furthermore, the proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable test execution speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of testing
infrastructure~---~led us to investigate if and how parallelization
features from testing frameworks and build systems are used in
practice.

@@

Each dimension focuses on one aspect of our study.  The first
dimension measures to which extent open-source projects contain time
costly test suites.  In the limit, parallelization will be fruitless
if all project contain short-running test suites The second dimension
measures how often open-source projects, irrespective of their
associated testing costs, use parallelization schemes.  This dimension
is concerned with popularity of parallelization.  The third aspect
evaluates the observed impact of parallelization on cost.  Finally,
the last dimension evaluates the issues and benefits associated with
running test suites with different parallel configuration (/modes).
Overall, the study of these dimensions help us layout the current
state-of-the-practice in usage of parallelization in open-source
projects.

@@

%%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
%%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
%%  LocalWords:  Ekstazi github CloudBuild PWA groupon criticality

%%% Local Variables:
%%% TeX-master: "main"
%%% End:
%%  LocalWords:  jenkins

>>>>

At large organizations, the alternative of renting cloud
services\footnote{List of popular hosting cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures to running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware (\eg{}, existing workstations), emerges as an attractive
solution for running tests.  Furthermore, the proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable test execution speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of relatively inexpensive
testing infrastructures~---~led us to investigate the usage of
parallelism for running tests in public open-source projects.

@@

Each dimension focuses on one aspect of our study.  The first
dimension measures to which extent open-source projects contain time
costly test suites.  In the limit, parallelization will be fruitless
if all projects contain short-running test suites. The second dimension
measures how often open-source projects, irrespective of their
associated testing costs, use parallelization schemes.  This dimension
is concerned with popularity of parallelization.  The third aspect
evaluates the observed impact of parallelization on cost.  Finally,
the last dimension evaluates the issues and benefits associated with
running test suites with different parallel configurations (/modes).
Overall, the study of these dimensions help us layout the current
state-of-the-practice about the use and impact of parallelization in open-source
projects, which presumably do not have large budgets.

@@

%%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
%%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
%%  LocalWords:  Ekstazi github CloudBuild PWA groupon criticality VM

%%% Local Variables:
%%% TeX-master: "main"
%%% End:
%%  LocalWords:  jenkins API VMs datarace
